Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
d

\section{Analysis}
A number of features are excluded before the training of the model. The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the valuation price. A list of the excluded features are found in appendix 11.0.1. The model used for ML are found in appendix 11.0.2.

The initial 10-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields.
\begin{table}[h!]
\begin{center}
\caption{Optimal hyperparameters\label{time}}
\begin{tabular}{ c  c  c } 
   $\lambda_{Lasso}$ & $\lambda_{Ridge}$ &  $\lambda_{Elastic Net}$ \\ \hline
   1 & 1 & 1 \\ \hline
\end{tabular}
\end{center}
\end{table} 
The prediction-error of each model

\begin{table}[h!]
\begin{center}
\caption{Prediction Errors\label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & Lasso & \, Ridge \ & \ Elastic Net \ & OLS \\ \hline
   MSE & 60,103,955,188.37 & \ 55,667,264,851.14 \  & \ 85,824,334,267.16 \ & 2.848e+28 \\ \hline
  RMSE & 245,161.08 & 235,939.11 & 292,957.91 & 168,763,945,674,352.3 \\ \hline
   MAE & 47,126.43 & 43,630.55 & 69,582.56 & 2,637,476,978,906.39 \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

@@

Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}. Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]

@@

\newpage
\section{Appendixs}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction
$$ \hat{Y_i}=\alpha+\hat{\beta}^T\textbf{X}_i+\hat{\epsilon_i}$$
$$\textbf{X}_i=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primarySchool\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\end{document}

>>>>

\section{Analysis}
A number of features are excluded before training the model. The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the valuation price. A list of the excluded features are found in appendix 11.0.1. The model used for ML are found in appendix 11.0.2.

The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields. 
\begin{table}[h!]
\begin{center}
\caption{Optimal hyperparameters, two degrees polynomial features\label{time}}
\begin{tabular}{ c | c  c  c } 
  & $\lambda_{Lasso}$ & $\lambda_{Ridge}$ &  $\lambda_{Elastic Net}$ \\ \hline
2 degrees  & 372.76 & 26.83 & 1 \\ \hline
3 degrees  & 2310.13 & 432.88 & 1
\end{tabular}
\end{center}
\end{table}

The prediction-errors of each model, with two and three degrees of polynomial features respectively, are printed below:
\begin{table}[H]
\begin{center}
\caption{Prediction Errors. \label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
   Lasso 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
  Ridge 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
  Elastic net 2-deg & 1 & 1 & 1  \\ 
  OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
  Lasso 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
  Ridge 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
  Elastic Net 3-deg & 1 & 1 & 1  \\
  OLS 3-deg & 2.848e+28 & 168,763,945,674,352.3 & 2,637,476,978,906.39  \\ \hline
\end{tabular}
\end{center}
\end{table}
The Ridge model with three degrees of polynomial features are selected as the best performing model. Both according to MAE

\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=1]{ValCurveRidge3deg.png}
%\source{}
\end{figure}

@@

\subsection{Model Selection}
Instead of only assessing the different models by MAE and RMSE.
The Information criteria of the respective models could have been introduced. Which could have altered the selection of preferred model. Both AIC and BIC, would likely have suggested Lasso, with 2-degrees of polynomial features, as preferred model. As both measurement are increasing in numbers of estimated parameters.

@@

Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}. Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]\newline

Peckov, Aleksandar. (2012)  \textit{A Machine Learning Approach To Polynomial Regression}. Available at \href{http://kt.ijs.si/theses/phd_aleksandar_peckov.pdf}{kt.ijs.si/theses/phd\_aleksandar\_peckov.pdf}. Doctoral Dissertation. Jozef Stefan International Postgraduate School. Ljubljana, Slovenia, October 2012

@@

\newpage
\section{Appendixs}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction: 
$$ \hat{Y_i}=\beta_0+\sum_{i=1}^n\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^mX_j^{d_i,j}
\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 9}$$
\small{$m$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
$$\textbf{X}_j=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primary\_school\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\end{document}
